Forecasting interrupted time series

### 2024-01-06 fits.tex
Recompiled

We apply the four solutions discussed in Section~\ref{sec-methods}. We
fit ETS, ARIMA and dynamic ARIMA models to the data, with no
transformations used. We have evaluated the methods by using time series
cross-validation, with the initial training set comprising the whole of
2019, and subsequent training sets growing by 1 week at a time, to the
end of 2021. The test sets are always 3 weeks long. Thus, we have
evaluated the forecasts during 2020 and 2021, covering all lockdown
periods, and the start of the recovery period. The results are shown in
\textbf{?@fig-walkers-plot1}.

@@

\includegraphics{fits_files/figure-pdf/unnamed-chunk-10-1.pdf}

>>>>

We apply the four solutions discussed in Section~\ref{sec-methods}. We
fit ARIMA and dynamic ARIMA models to the data, with no transformations
used. We have evaluated the methods by using time series
cross-validation, with the initial training set comprising the whole of
2019, and subsequent training sets growing by 1 week at a time, to the
end of 2021. The test sets are always 1 week long. Thus, we have
evaluated the forecasts during 2020 and 2021, covering all lockdown
periods, and the start of the recovery period. The results are shown in
Figures \ref{fig-walkers-plot1}--\ref{fig-walkers-plot4}

\includegraphics{fits_files/figure-pdf/fig-walkers-plot1-1.pdf}

\caption{\label{fig-walkers-plot1}Solution 1: the forecasts do not take
into account the lockdown periods, but the ARIMA model is able to adjust
to the changing level of the series.}

\includegraphics{fits_files/figure-pdf/fig-walkers-plot2-1.pdf}

\caption{\label{fig-walkers-plot2}Solution 2: the forecasts are based on
an ARIMA model with a dummy variable indicating when the lockdown
periods occurred.}

\includegraphics{fits_files/figure-pdf/fig-walkers-plot3-1.pdf}

\caption{\label{fig-walkers-plot3}Solution 3: the lockdown periods are
set to missing, and the ARIMA model uses the remaining data to produce
forecasts}

\includegraphics{fits_files/figure-pdf/fig-walkers-plot4-1.pdf}

\caption{\label{fig-walkers-plot4}Solution 4: the lockdown periods are
replaced with estimated counts based on an ARIMA model applied to the
remaining data. Then a new ARIMA model is fitted to the whole data set,
and used to produce forecasts.}

@@

\includegraphics{fits_files/figure-pdf/unnamed-chunk-14-1.pdf}
